The Unintended Consequences of Energy Reduction

### 2024-02-15 paper/paper.qmd
Cleaned up sections and editted intro

@@

![Figure 1](../other/figures/figure1.png)
![Figure 3](../other/figures/figure3.png)
![Figure 4](../other/figures/figure4.png)

After the Fukushima incident, the government tried to ensure sufficient backup capacity to avoid power blackouts. While other factors could affect the saving target, the primary determinant of the saving target was a region’s dependence on nuclear power before the accident.(Kim, et al.) This caused more health issues for individuals as they were encouraged to not use AC and other cooling devices during hotter days. Previous to the implementation of the energy policy, throughout the period between 1960 and 2004, the mortality rate was significantly lower (closer to 0.87) while the mortality rate after was much higher (close to 0.95)[figure 3]. In addition, the mortality rate for heatstrokes also increased dramatically in the year 2011 more than doubling that of 2010.
Moreover, the mortality risk caused by electricity saving is particularly high in the summer, during which the energy-saving campaigns are intensively promoted. To account for the potential “harvesting effect” or “delayed effect,” we also estimate distributed lag models on the impacts of temperature and the energy-saving policy. Taking into account this dynamic impact, it is estimated that the energy-saving campaigns could have led to nearly 7,710 premature deaths annually in Japan (Kim, et al.).
Lastly, there is a trend where the higher the saving targets, the higher the increase in the mortality rate during the hot days (between 25–30°C and above 30°C), but a relatively moderate increase for cold temperatures (below 0°C and 0–5°C) (Kim et. al).

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

@@

@@

# Results
Based on the temperature summary data, it's observed that Summers can get quite hot with highs of over 32 degrees Celsius. That alongside rising electricity prices over the analysed period (mean > median) and an implementation of an energy conservation target. It's easy to deduce the likely hood of an extreme increase in heatstrokes with the mean people transported sitting at almost four times the median. 
When observing data between temperature and energy usage, there should be a correlation between extreme weather and energy use. As cold weather would prompt higher usage of heaters while hot weather would prompt higher usage of AC. Post Fukushima, the energy usage did not keep up with the extreme weather which took a toll on different aspects such as higher number of heatstroke victims and increased mortality rate.
Furthermore, with respect to energy consumption data, there is an extremely high third quantile of almost 6.5 million MWH which suggests higher ranges of energy consumption. This can be indicative of overuse of energy resources, perhaps stemming from an abrupt switch from nuclear energy to fossil fuels.
Finally, all of this is reflective in the massive energy price fluctuations of around 13 yen per MWH to over 23 yen. These fluctuations are indicative of a very unstable energy market which can be the results of the energy source shift and the energy policy.

>>>>

The government's energy-saving policies included energy-saving targets to be met. While many factors could affect the saving target, the primary determinant of the saving target was a region’s dependence on nuclear power before the accident (Kim, et al.) This caused more health issues for individuals as they were encouraged to not use air conditioning and other cooling devices during hotter days. Prior to the implementation of the energy policy, throughout the period between 1960 and 2004, the mortality rate during high temperatures was significantly lower (closer to 0.87) while the mortality rate after was much higher (close to 0.95) [see Figure 3]. In addition, the mortality rate for heat strokes increased dramatically in the year 2011 more than doubling that of 2010.
Moreover, the mortality risk caused by electricity saving is particularly high in the summer, during which the energy-saving campaigns are intensively promoted. To account for the potential “harvesting effect” or “delayed effect,” we also estimate distributed lag models on the impacts of temperature and the energy-saving policy. Taking into account this dynamic impact, it is estimated that the energy-saving campaigns could have led to nearly 7,710 premature deaths annually in Japan (Kim, et al.). Furthermore, there is a trend where the higher the saving targets, the higher the increase in the mortality rate during the hot days (between 25–30°C and above 30°C), but a relatively moderate increase for cold temperatures (below 0°C and 0–5°C) (Kim et. al).

@@

@@

## Sources

To create our figures and reproduce figures from *Energy Saving May Kill: Evidence from the Fukushima Nuclear Accident* by He and Tanaka (2019), the statistical programming language R was used to acquire, clean, and process the data [@citeR]. In particular, the following R packages were used: tidyverse [@tidyverse], readxl [@readxl], haven [@haven], ggthemes [@ggthemes], and ggplot2 [@ggplot2].

## Variables and Measurement

@@

\newpage
# Results
![](../other/figures/figure1.png)
\newpage
![](../other/figures/figure2.png)
\newpage
![](../other/figures/figure3.png)
\newpage
![](../other/figures/figure4.png)
\newpage
![](../other/figures/figure5.png)

Based on the temperature summary data, it's observed that Summers can get quite hot with highs of over 32 degrees Celsius. That alongside rising electricity prices over the analysed period (mean > median) and an implementation of an energy conservation target. It's easy to deduce the likely hood of an extreme increase in heatstrokes with the mean people transported sitting at almost four times the median. 
When observing data between temperature and energy usage, there should be a correlation between extreme weather and energy use. As cold weather would prompt higher usage of heaters while hot weather would prompt higher usage of AC. Post Fukushima, the energy usage did not keep up with the extreme weather which took a toll on different aspects such as higher number of heatstroke victims and increased mortality rate.
Furthermore, with respect to energy consumption data, there is an extremely high third quantile of almost 6.5 million MWH which suggests higher ranges of energy consumption. This can be indicative of overuse of energy resources, perhaps stemming from an abrupt switch from nuclear energy to fossil fuels.
Finally, all of this is reflective in the massive energy price fluctuations of around 13 yen per MWH to over 23 yen. These fluctuations are indicative of a very unstable energy market which can be the results of the energy source shift and the energy policy.
